Endogenous Politics and \\ the Design of Trade Institutions

### 2016-07-21 feedback.tex
add feedback from 2015 CEAs
add devashish's feedback after SITE

\subsection{From SITE 2016 presentation}
\begin{itemize}
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with contributions 'felonious'
	\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
		\begin{itemize}
			\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
			\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
		\end{itemize}
	\item $\ga(e)$
		\begin{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
		\end{itemize}
	\item Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies
		\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether
		\end{itemize}
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Bob and Kyle: take my time, make it as good as possible. Better to have quality.
\end{itemize}

@@

\newpage
\subsection{January 2016, PEIO Salt Lake City}
\begin{itemize}
	\item Elias Bengtsson: more on policy implications, who's doing what to whom
	\item Cristiane Carneiro
		\begin{itemize}
			\item Flexible instruments
			\item Agreement duration, exit (legal scholarship)
			\item Look at Summer 2001 special edition of IO
			\item Korgmenos 2013 JCR
			\item Korgmenos and Nav 2011
			\item Coil
			\item Helper 2005, Virginia Law Review
		\end{itemize}
	\item Renee Bowen: what's the contribution relative to GH; her paper, Peter's, McLaren (but she was a bit confused about what I was doing we figured out later)
	\item Competing lobbies--exporters
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover
\end{itemize}

>>>>

\subsection{From SITE 2016 presentation}
\begin{itemize}
	\item Kyle: McLaren in his chapter calls the Grossman and Helpman setup with contributions 'felonious'
	\item Kyle: why doesn't government (dis)value expenditure by lobby? Needs to be counted in government welfare function or justify why not
		\begin{itemize}
			\item Rohan: $(1-a)\cdot C + a \cdot W \equiv C + a \cdot (W-C)$
			\item When weights on $\pi_X$ are not linear, what are the implications for resource waste? Is it the same as $+ C / - C$?
			\item Devashish: Utility fcn didn't change. Just got evaluated at a different point
				\begin{itemize}
					\item Preferences don't change. It's persuasion that affects decision-making. 2nd story: Giovanni's
					\item Find something in persuasion literature
				\end{itemize}
		\end{itemize}
	\item $\ga(e)$
		\begin{itemize}
			\item Giovanni: think of expost $\ga(e)$ as effort to elect/choose ex-post decision-maker
			\item At worst, I can use leg / exec split to deal with this criticism
			\item Kyle (???): advertising paper (???)
			\item Mostafa, Nuno, Giovanni, Anson to some extent: Cardinal vs. ordinal
				\begin{itemize}
					\item Giovanni: if I can show properties survive  monotonic transformation, I'm fine
					\item They don't like gov't choosing its own preferences. May just need to change wording
				\end{itemize}
			\item Bob: what is fundamental structure of preferences?
			\item The way $e$ affects preferences doesn't change!!! Preferences are wrapped up in $\ga$!
		\end{itemize}
	\item Bob: maybe gov't has some other reason for setting non-zero tariff that opens the door for lobbies. 2nd best remedy for market failure, etc.
		\begin{itemize}
			\item Maybe I should just get rid of tariff cap result altogether
		\end{itemize}
	\item David DeRemer: Safeguards have dropped off in use around the world
		\begin{itemize}
			\item Look at U.S. vs. ROW (he sent papers)
		\end{itemize}
	\item I think that I need to bring people along more carefully from GH/MRC to what I'm doing
	\item Bob and Kyle: take my time, make it as good as possible. Better to have quality.
\end{itemize}

@@

\newpage
\subsection {Summer 2015 CEA}
\begin{itemize}
	\item Richard: what happens if $\ga(e^L) < \ga(s^H)$?
	\item Dev: Reputation: do they use safeguards less b/c worried about reputation?
	\item Chris: What is an exogenous shock to political pressure? What signal would be correlated?
\end{itemize}

\vskip.5in
\subsection{January 2016, PEIO Salt Lake City}
\begin{itemize}
	\item Elias Bengtsson: more on policy implications, who's doing what to whom
	\item Cristiane Carneiro
		\begin{itemize}
			\item Flexible instruments
			\item Agreement duration, exit (legal scholarship)
			\item Look at Summer 2001 special edition of IO
			\item Korgmenos 2013 JCR
			\item Korgmenos and Nav 2011
			\item Coil
			\item Helper 2005, Virginia Law Review
		\end{itemize}
	\item Renee Bowen: what's the contribution relative to GH; her paper, Peter's, McLaren (but she was a bit confused about what I was doing we figured out later)
	\item Competing lobbies--exporters
	\item Peter: $\ga(e)$ and $\ga(s)$ combination is interesting, so it dyanmic choice of protection over time, gov't turnover
\end{itemize}
